---
title: "R Markdown Document Template"
subtitle: "Georgia Tech, MGT 6203, Data Analytics in Business, Summer 2020"
author: "Ramin Melikov, melikov@gatech.edu"
date: '`r format(as.POSIXct(Sys.Date()), "%B %d, %Y", tz = "America/Chicago")`'
output:
  html_document:
    toc: true
    theme: journal
    highlight: tango
editor_options:
  chunk_output_type: console
---


# R and Python in R Markdown

## Variables get passed from code chunk to code chunk

### Setup

**We'll need the `reticulate` package. Enable the code chunk to install the package. (Set `eval = TRUE`.)**
```{r eval = FALSE}
install.packages("reticulate")
```

**Let's now use the `reticulate` package.**
```{r}
library(reticulate)
```

### Start in R

**First, we're using R to create a secret.**
```{r}
secret <- "RPythonMarkdown"
```

### Go to Python

**Next, we're passing the secret from R to Python. (Variable `secret` from `r`.)**
```{python}
secret = r.secret
```

### Back in R

**And finally, we're checking in R if `py$secret == secret`. (Variable `secret` from `python`.)**
```{r}
if (py$secret == secret) {
  "Hello, World!"
}
```

**All done!**
